---
title: "Ch 7_Answers"
author: "Kathleen Johnson"
date: "9/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

```
```{r}
data("diamonds")
```
```{r}
str(diamonds)
```

Explore the distribution of each of the x, y, and z variables in diamonds. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5)+
  coord_cartesian(ylim = c(0, 50))

```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = x))+
  coord_cartesian(ylim = c(0,1000))
```
```{r}
summary(diamonds$x)
```

```{r}
str(diamonds$z)
```
```{r}
summary(diamonds$z)
```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = z))+
  coord_cartesian(xlim = c(1,8))
```

Explore the distribution of price. Do you discover anything unusual or surprising?

```{r}
summary(diamonds$price)

```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = price))
```

There are more priced on the lower side as opposed to higher which may be an indicator of customer base. What I mean by that is, are more of the individuals buying diamonds only able to afford the lower cost ones?

```{r}
str(diamonds$carat)
```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = carat))
```

```{r}
count(diamonds, carat)
```

How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference? (I don't think I did this right)

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5) +
  coord_cartesian(ylim = c(0, 50))
```

Compare and contrast coord_cartesian() vs xlim() or ylim() when zooming in on a histogram. What happens if you leave binwidth unset? What happens if you try and zoom so only half a bar shows?

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y)) +
  coord_cartesian(xlim = c(0, 20))
```

What happens if you try and zoom so only half a bar shows? - not sure how to do this. 

```{r}
diamonds2 <- diamonds %>% 
  mutate(y = ifelse(y < 3 | y > 20, NA, y))
```

```{r}
ggplot(data = diamonds2, mapping = aes(x = x, y = y)) + 
  geom_point(na.rm = TRUE)
```

What happens to missing values in a histogram? What happens to missing values in a bar chart? Why is there a difference?
```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y))
```
```{r}
ggplot(diamonds2) + 
  geom_histogram(mapping = aes(x = y))
```
The histogram was "zoomed" in to just looking at y(0,11) 

```{r}
ggplot(data = diamonds) +
  geom_bar(mapping = aes(x = cut))
```
```{r}
ggplot(data = diamonds2) +
  geom_bar(mapping = aes(x = cut))
```
I don't see a difference with the bar chart, but there may not be missing data in the variable cut?

What does na.rm = TRUE do in mean() and sum()?

```{r}
mean(diamonds$carat)
```

```{r}
mean(diamonds$carat)+(na.rm = TRUE)
```

Why are the numbers different when doing na.rm = TRUE?

```{r}
sum(diamonds$carat)
```

```{r}
sum(diamonds$carat)+(na.rm = TRUE)
```

