---
title: "Ch 7_Answers"
author: "Kathleen Johnson"
date: "9/16/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)

```
```{r}
data("diamonds")
```
```{r}
str(diamonds)
```

Explore the distribution of each of the x, y, and z variables in diamonds. What do you learn? Think about a diamond and how you might decide which dimension is the length, width, and depth.

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = y), binwidth = 0.5)+
  coord_cartesian(ylim = c(0, 50))

```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = x))+
  coord_cartesian(ylim = c(0,1000))
```
```{r}
summary(diamonds$x)
```

```{r}
str(diamonds$z)
```
```{r}
summary(diamonds$z)
```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = z))+
  coord_cartesian(xlim = c(1,8))
```

Explore the distribution of price. Do you discover anything unusual or surprising?

```{r}
summary(diamonds$price)

```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = price))
```

There are more priced on the lower side as opposed to higher which may be an indicator of customer base. What I mean by that is, are more of the individuals buying diamonds only able to afford the lower cost ones?

```{r}
str(diamonds$carat)
```

```{r}
ggplot(diamonds) + 
  geom_histogram(mapping = aes(x = carat))
```

```{r}
count(diamonds, vars= carat, wt_var=.99)
```

How many diamonds are 0.99 carat? How many are 1 carat? What do you think is the cause of the difference? (I don't think I did this right)


